A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-19 tex/body.tex
more
whitespace
avoid ugly abbrev

\begin{table*}[t!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}cc@{\kern.5em}cc@{\kern.5em}cc@{\kern1.3em}cc@{\;}}
  & \multicolumn{2}{c}{Distro} & \multicolumn{2}{c}{AFP} & \multicolumn{2}{c}{\gandl} & \multicolumn{2}{c}{Overall} \\
  & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4}
\MIDRULE
No (co)datatypes
  & 209 & 221 & 777 & 775 & 51 & 52 & 1037 & 1048 \\%[\jot]
%Datatype simplification only
%  &  \\
Datatypes w/o \rn{Acyclic}
  & -- & 227 & -- & 780 & -- & 52 & -- & 1059 \\
Full datatypes
  & 213 & 227 & 791 & 786 & 51 & 52 & 1055 & 1065 \\%[\jot]
%Codatatype simplification only
%  &  \\
Codatatypes w/o \rn{Unique}
  & -- & 222 & -- & 804 & -- & 56 & -- & 1082 \\
Full codatatypes
  & -- & 223 & -- & 804 & -- & \bfseries 59 & -- & 1086 \\%[\jot]
Full (co)datatypes
  & -- & \bfseries 229 & -- & \bfseries 815 & -- & \bfseries 59 & -- & \bfseries 1103% \\[\jot]
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

@@

This work is part of a program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving. As future work, it would be useful to implement
proof reconstruction for (co)data\-type inferences in Isabelle. We also
want to try out CVC4 for model finding in Isabelle, as an alternative to
Nitpick. Finally, it might be worthwhile to extend SMT solvers with dedicated
support for (co)recursive functions.

>>>>

\begin{table*}[t!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}cc@{\kern.5em}cc@{\kern.5em}cc@{\kern1.3em}cc@{\;}}
  & \multicolumn{2}{c}{Distro} & \multicolumn{2}{c}{AFP} & \multicolumn{2}{c}{\gandl} & \multicolumn{2}{c}{Overall} \\
  & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4}
\MIDRULE
No (co)datatypes
  & 209 & 221 & 777 & 775 & 51 & 52 & 1037 & 1048 \\%[\jot]
%Datatype simplification only
%  &  \\
Datatypes without \rn{Acyclic}
  & -- & 227 & -- & 780 & -- & 52 & -- & 1059 \\
Full datatypes
  & 213 & 227 & 791 & 786 & 51 & 52 & 1055 & 1065 \\%[\jot]
%Codatatype simplification only
%  &  \\
Codatatypes without \rn{Unique}\!\!
  & -- & 222 & -- & 804 & -- & 56 & -- & 1082 \\
Full codatatypes
  & -- & 223 & -- & 804 & -- & \bfseries 59 & -- & 1086 \\%[\jot]
Full (co)datatypes
  & -- & \bfseries 229 & -- & \bfseries 815 & -- & \bfseries 59 & -- & \bfseries 1103% \\[\jot]
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

@@

This work is part of a program that aims at enriching automatic provers
with high-level features and at reducing the gap between automatic and
interactive theorem proving. As future work, it would be useful to implement
proof reconstruction for (co)data\-type inferences in Isabelle.
CVC4 cound be interfaced for generating counterexamples in proof assistants, as
an alternative to Nitpick. Finally, it might be worthwhile to extend SMT solvers
with dedicated support for (co)recursive functions.
